The locations of features in the mass distribution of merging binary black holes are robust against uncertainties in the metallicity-dependent cosmic star formation history.

### 2023-02-06 src/tex/article.tex
removed surplus tex data and updated zenodo link in article.tex

We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson2022_lowMbh}.\footnote{Available for download at \url{https://sandbox.zenodo.org/record/1101303},  see also the Software and Data section in the acknowledgements}  
These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}. \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}. \edit1{In particular, we use the simulations behind Figure 1 from \cite{vanson2022_lowMbh}, and we refer the reader to their methods section for a detailed description of the adopted physics parameters and assumptions.}\footnote{ \edit1{ We note that the rate in \cite{vanson2022_lowMbh} is slightly higher than the fiducial rate presented in Figure \ref{fig: stable mass dists} in this work. This difference is caused by the use of rounded parameter values of \SFRDzZ in \cite{vanson2022_lowMbh}.} } % In particular the value of $\mu_z$ has a significant effect on the inferred rate for the stable channel.} 
%
Metallicities of each binary system were sampled from a smooth probability distribution to avoid artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}. 
These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity.

@@

\section*{Software and Data}
% Code and Data 
All code associated to reproduce the data and plots in this paper is publicly available at \url{https://github.com/LiekeVanSon/SFRD_fit}.
The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[10.5072/zenodo.1101303]{https://sandbox.zenodo.org/record/1101303}.
% \dataset[doi:10.5281/zenodo.5544170]{https://doi.org/10.5281/zenodo.5544170}.
All observationally constrained models of the \SFRDzZ from \cite{Chruslinska+2021} can be found online at: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}.

>>>>

We use the publicly available rapid binary population synthesis simulations presented in \cite{vanson2022_lowMbh}.\footnote{Available for download at \url{https://zenodo.org/record/7612755},  see also the Software and Data section in the acknowledgements}  
These simulations were run using version v02.26.03 of the open source \COMPAS suite \citep{COMPAS_method}\footnote{\url{https://github.com/TeamCOMPAS/COMPAS}}. \COMPAS is based on algorithms that model the evolution of massive binary stars following \citet{Hurley+2000, Hurley+2002} using detailed evolutionary models by \citet{Pols+1998}. \edit1{In particular, we use the simulations behind Figure 1 from \cite{vanson2022_lowMbh}, and we refer the reader to their methods section for a detailed description of the adopted physics parameters and assumptions.}\footnote{ \edit1{ We note that the rate in \cite{vanson2022_lowMbh} is slightly higher than the fiducial rate presented in Figure \ref{fig: stable mass dists} in this work. This difference is caused by the use of rounded parameter values of \SFRDzZ in \cite{vanson2022_lowMbh}.} } % In particular the value of $\mu_z$ has a significant effect on the inferred rate for the stable channel.} 
%
Metallicities of each binary system were sampled from a smooth probability distribution to avoid artificial peaks in the BH mass distribution \citep[e.g.][]{Dominik2015,Kummer_thesis}. 
These simulations provide us with an estimate of the yield of BBH mergers per unit of star-forming mass and metallicity.

@@

\section*{Software and Data}
% Code and Data 
All code associated to reproduce the data and plots in this paper is publicly available at \url{https://github.com/LiekeVanSon/SFRD_fit}.
The data used in this work is available on Zenodo under an open-source Creative Commons Attribution license at \dataset[10.5281/zenodo.7612755]{https://zenodo.org/record/7612755}.
All observationally constrained models of the \SFRDzZ from \cite{Chruslinska+2021} can be found online at: \url{https://ftp.science.ru.nl/astro/mchruslinska/Chruslinska_et_al_2021/}.
